Analysis

### 2021-02-25 results.tex
update the script to report the results of the three executions

\begin{table}[ht]
  \caption{Summary of the results of the first study. }
  \centering
  \begin{small}
 \begin{tabular}{lrrr}
   \toprule
   Tool & Exec. (WS) & Exec. (WOS) & Impact (\%) \\   \midrule
  Monkey &  71 &  54 & 23.94 \\ 
  DroidMate &  64 &  48 & 25.00 \\ 
  DroidBot &  68 &  54 & 20.59 \\ 
  Humanoid &  49 &  15 & 69.39 \\ 
  \joke &  42 &   0 & 100.00 \\ 
 \bottomrule
 \end{tabular}
 \end{small}
 \label{tab:fs}
\end{table}

>>>>

\begin{table}[ht]
  \caption{Summary of the results of the first study. }
  \centering
  \begin{small}
 \begin{tabular}{lrrr}
   \toprule
   Tool & Exec. (WS) & Exec. (WOS) & Impact (\%) \\   \midrule
   DroidBot &  73 & 61.00 & 16.44 \\ 
   Monkey &  71 & 56.00 & 21.13 \\ 
   DroidMate &  68 & 52.00 & 23.53 \\ 
   Humanoid &  56 & 27.00 & 51.79 \\ 
\joke &  42 & 0.00 & 100.00 \\ 
 \bottomrule
 \end{tabular}
 \end{small}
 \label{tab:fs}
\end{table}

### 2021-02-25 results/script.Rmd
update the script to report the results of the three executions

---
title: "Analysis"
output: html_document
---

@@

## Load the Summary Dataset for Study 1

```{r}
ds <- read.csv("./execution01.csv", head=T, sep=",")
ds["Improvement"] = (ds$WithDroidFax - ds$WithoutDroidFax) * 100 / ds$WithDroidFax
xtable(ds)
```

@@

```{r venn-plot-s1}
ds <- read.csv("./report_withStatic.csv", head=T, sep=",")

sets <- sqldf("select tool, app from ds where malware = 'True'")
monkey = sets[sets$tool=="monkey", c("app")]
humanoid = sets[sets$tool=="humanoid", c("app")]
droidmate = sets[sets$tool=="droidmate", c("app")]
droidbot = sets[sets$tool=="droidbot", c("app")]
joker = sets[sets$tool=="joke", c("app")]

venn.diagram(
  x = list(monkey, humanoid, droidmate, droidbot, joker),
  category.names = c("Monkey" , "Humanoid" , "DroidMate", "DroidBot", "Joker"),
  filename = './venn.png',
  output=TRUE
)

@@

```{r}
sqldf("select count(distinct app) from ds where malware = 'True'")
```

@@

```{r venn-plot-s2}
 ds <- read.csv("allreportResults.csv", head=T, sep=",")
sets <- sqldf("select tool, app 
                  from ds 
                  where malware = 1 
                    and (tool='flowdroid' or tool = 'joke')")

@@

# subsets
notDetected

>>>>

---
title: "Analysis"
output:
  html_document: default
  pdf_document: default
---

@@

@@

```{r}
ds <- read.csv("allreportResults.csv", head=T, sep=",")

staticAnalysis <- sqldf("select tool, count(distinct app) totalWith
                        from ds 
                        where malware = 1 and static = 1 and tool != 'flowdroid'
                        group by tool")

withoutStaticAnalysis <-  sqldf("select tool, count(distinct app) totalWithout
                                  from ds 
                                  where malware = 1 and static = 0
                                  group by tool")

res <- merge(staticAnalysis, withoutStaticAnalysis, all.x=T)

res[is.na(res)] <- 0
res["Improvement"] = (res$totalWith  - res$totalWithout) * 100 / res$totalWith 
xtable(res[order(-res$totalWith),])
```

## Compare the performance of the different tools (with DroidFax)

```{r, venn-plot-s1}

colnames(ds)
sets <- sqldf("select tool, app, count(*) total 
                  from ds 
                  where malware = 1 and static = 1
                  group by tool, app")

monkey = sets[sets$tool=="monkey", c("app")]
humanoid = sets[sets$tool=="humanoid", c("app")]
droidmate = sets[sets$tool=="droidmate", c("app")]
droidbot = sets[sets$tool=="droidbot", c("app")]
joker = sets[sets$tool=="joke", c("app")]

@@

```{r}
sqldf("select count(distinct app) from ds where malware = 1")
```

@@

```{r}
ds <- read.csv("allreportResults.csv", head=T, sep=",")
```

## Compare the performance of FlowDroid and DroidFax (Joker tool)

```{r, venn-plot-s2}
sets <- sqldf("select tool, app 
                  from ds 
                  where malware = 1 
                    and (tool='flowdroid' or tool = 'joke')")

@@
